---
title: "Codebook"
author: "Mario"
date: "2025-07-24"
output: html_document
---
# Varibles in tidydataset.txt
The cleaned dataset contains 69 variables and is saved in a text fixed width format.

## List of variables
Decriptive variables, detailing the volunteer and the activity that realized.

| Variable | Description                                |
|----------|--------------------------------------------|
| ID       | Subjects that participated. 30 volunteers. |
| ACT      | Code for six activities realized           |
| ACTnames | Name of activity realized                  |

Variables in XYZ dimensions, from which the mean and standard deviation were estimated:

| Variable          | Description                          | Instrument    | Domain    |
|-------------------|--------------------------------------|---------------|-----------|
| tBodyAcc-XYZ      | Body acceleration signal             | Accelerometer | Time      |
| tGravityAcc-XYZ   | Gravity acceleration signal          | Accelerometer | Time      |
| tBodyAccJerk-XYZ  | Body acceleration Jerk signal        | Accelerometer | Time      |
| tBodyGyro-XYZ     | Body angular velocity signal         | Gyroscope     | Time      |
| tBodyGyroJerk-XYZ | Body angular velocity jerk signal    | Gyroscope     | Time      |
| tBodyAccMag       | Body acceleration magnitude          | Accelerometer | Time      |
| tGravityAccMag    | Gravity acceleration magnitude       | Accelerometer | Time      |
| tBodyAccJerkMag   | Body acceleration jerk magnitude     | Accelerometer | Time      |
| tBodyGyroMag      | Body angular velocity magnitude      | Gyroscope     | Time      |
| tBodyGyroJerkMag  | Body angular velocity jerk magnitude | Gyroscope     | Time      |
| fBodyAcc-XYZ      | Body acceleration signal             | Accelerometer | Frequency |
| fBodyAccJerk-XYZ  | Body acceleration Jerk signal        | Accelerometer | Frequency |
| fBodyGyro-XYZ     | Body angular velocity signal         | Gyroscope     | Frequency |
| fBodyAccMag       | Body acceleration magnitude          | Accelerometer | Frequency |
| fBodyAccJerkMag   | Body acceleration jerk magnitude     | Accelerometer | Frequency |
| fBodyGyroMag      | Body angular velocity magnitude      | Gyroscope     | Frequency |
| fBodyGyroJerkMag  | Body angular velocity jerk magnitude | Gyroscope     | Frequency |


## Structure of tidydataset
Preview of the tidydataset
```{r}
library(data.table)
TTdata=fread("tidydataset.txt")
head(TTdata[,1:5],12)
```

Structure of the tidydataset
```{r}
str(TTdata)
```